The Globular Cluster System of the Auriga Simulations

### 2019-01-10 AurigaGCS.tex
Generate Mauriga/Mmilkyway in each of the 25 FeHRgc bins

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
    Wilma Trick$^{1}$,
    Robert J. J. Grand$^{1}$, 
    Volker Springel$^{1}$, 
    Facundo A. G\'{o}mez$^{2,3}$, 
    Federico Marinacci$^{4,5}$,
    R\"{u}diger Pakmor$^{1}$, 
    Simon D. M. White$^{1}$
} \vspace{10pt} \\
$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
    Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av.
    Juan Cisternas 1200 N, La Serena, Chile \\
$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
    MIT, Cambridge, MA 02139, USA \\
$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
    MA 02138, USA \\
}

@@

Look into Pandromeda survey? Star counts, very wide angle survey

@@

\subsection{Radius-metallicity distribution}
\label{sec:RgcFeH}
What age-metallicity distribution is produced by star formation events in the Auriga simulations?

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{logMRgcFeH_accreted-insitu-notitle}.png}
    \caption{
        OMG what a beautiful plot.
        \label{fig:todo2}
    }
\end{figure}

\section{Properties of birth haloes of the accreted population}
\label{sec:birth-properties-of-accreted-gc-candidates}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[T. L. R. Halbesma et al.]{\parbox[t]{\textwidth}{
    Timo L. R. Halbesma$^{1}$\thanks{E-mail: Halbesma@MPA-Garching.MPG.DE},
    Philipp Busch$^{1}$,
    Wilma Trick$^{1}$,
    Robert J. J. Grand$^{1}$, 
    Volker Springel$^{1}$, 
    Facundo A. G\'{o}mez$^{2,3}$, 
    Federico Marinacci$^{4,5}$,
    R\"{u}diger Pakmor$^{1}$, 
    Simon D. M. White$^{1}$
} \vspace{10pt} \\
$^{1}$ Max-Planck-Institut f\"ur Astrophysik, Postfach 1317, D-85741 Garching, Germany \\
$^{2}$ Instituto de Investigaci\'{o}n Multidisciplinar en Ciencia yTecnolog\'{i}a, 
    Universidad de La Serena, Ra\'{u}l Bitr\'{a}n 1305, La Serena, Chile \\
$^{3}$ Departamento de F\'{i}sica y Astronom\'{i}a, Universidad de La Serena, Av.
    Juan Cisternas 1200 N, La Serena, Chile \\
$^{4}$ Department of Physics, Kavli Institute for Astrophysics and Space Research,
    MIT, Cambridge, MA 02139, USA \\
$^{5}$ Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge,
    MA 02138, USA \\
}

@@

\todo[inline]{
Look into Pandromeda survey. Star counts, very wide angle survey
}

@@

\subsection{Radius-metallicity distribution}
\label{sec:RgcFeH}
What age-metallicity distribution is produced by star formation events in the Auriga simulations?
?
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-r$_{\text{gc}}$ distribution of all Auriga haloes 
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all 
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-RgcFeH}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{logMRgcFeH_accreted-insitu-notitle}.png}
    \caption{
        OMG what a beautiful plot - now only need 1$\sigma$ interval around both
        relations, and need to know exactly what model I fit...
        \label{fig:todo2}
    }
\end{figure}

\subsection{Properties of birth haloes of the accreted population}
\label{sec:birth-properties-of-accreted-gc-candidates}
